Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-12 docs/proposal/proposal.tex
minor work

In mathematics, a graph is usually modeled as \( G = (V, E) \), where \( V \) represents the set of vertices and \( E \) represents the set of edges between them.
A hypergraph is denoted as \( G_{H} = (V_{H}, E_{H}) \), where \( V_{H} \) represents the set of vertices, and \( E_{H} \) represents the set of hyperedges, which are edges that can connect more than two vertices.
Electronic circuits are typically represented as hypergraphs where % FINISH ME
In FPGA design, the graph is often modeled using a "netlist". A netlist is a graph \( G = (V, E) \), where \( V \) represents the components (e.g., logic blocks or gates), and \( E \) represents the connections or nets between them.

The vast majority of existing placers use the Half Perimeter Wire Length (HPWL) cost function or one of its various flavors - manhattan distance, euclidian distance, beta-regularized, etc..
The basic HPWL models the problem as the summation of the manhattan lengths of all nets in the netlist.

@@

Then, the paper will survey the current landscape of placement algorithms and strategies. 
This includes Simulated Annealing (SA), Analytical Placement (AP),

>>>>

In mathematics, a graph is modeled as \( G = (V, E) \), where \( V \) represents the set of vertices and \( E \) represents the set of edges between them.
A hypergraph is denoted as \( G_{H} = (V_{H}, E_{H}) \), where \( V_{H} \) represents the set of vertices, and \( E_{H} \) represents the set of hyperedges, which are edges that can connect more than two vertices.
Electronic circuits are represented as hypergraphs as because a voltage source can have one or many sinks. 
In FPGA design, the hypergraph is often transform into something called a "netlist", which is a hypergraph that has been flattened down into a graph. 
For every hyperedge in the hypergraph, transform the hyperedge into a collection of 2-pin edges - one source to one sink.
There are different strategies for this reduction - unoriented star model, clique model, etc.. 
A netlist is a graph \( G = (V, E) \), where \( V \) represents the components (e.g., logic blocks or gates), and \( E \) represents the connections or nets between them.

The vast majority of existing placers use the Half Perimeter Wire Length (HPWL) cost function or one of its various flavors - manhattan distance, euclidian distance, beta-regularized, etc..
The basic HPWL models the cost function as the summation of the manhattan lengths of all nets in the netlist.

This paper will primarily use Xilinx's open-source API, RapidWright to implement various custom placement algorithms.
RapidWright is a Java API that provides backend access to Xilinx's EDA, Vivado.

@@

Then, the paper will survey the current landscape of placement algorithms and strategies. 
This includes Simulated Annealing (SA) which is stochastic, but will focus on Analytical Placement (AP).
